How One Microtask Affects Another

### 2016-01-08 docs/publications/2015.12_CHI/man.tex
camera ready for chi

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is      granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

@@

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead 
%\usepackage[T1]{fontenc}
\usepackage{txfonts}
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage[pdftex]{hyperref}
% \usepackage{url}      % llt: nicely formatted URLs
\usepackage{color}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{ccicons}
\usepackage{todonotes}

@@

@@

\numberofauthors{1}
\author{%
  \alignauthor{
	Authors\\
    \affaddr{Affiliations}\\
    \affaddr{Addresses 	}\\
	\email{email@domain.com}
  }\\
  %\alignauthor{
  %  Author 2 \\
  %  \affaddr{Affiliation 1}\\
  %  \affaddr{Montreal, Qu\'ebec,
  %    Canada
  %  }\\
  %  \email{derek.ruths@mcgill.ca}
  %}\\
}

@@

Psychological experiments show that the exposure to stimuli immediately 
before performing a task influences performance, an effect known as 
\textit{priming} \cite{BJOP1796}.
The effect of priming appears to be stronger when the modality of the
prime is the same as the task.
Thus, for the typical microtask worker, who does many similar tasks in
quick succession, there is a potential for earlier tasks to influence
later ones, via priming or other mechanisms.

@@

As our main contributions, we
\begin{itemize}[noitemsep,nolistsep]
  \item{
	derive a method for measuring changes in response distributions;
  }
  \item{measure the strength of intertask effects;}
  \item{show that intertask effects are stronger than,
	or on par with framing;}
  \item{
	show that when completing a series of similar microtasks,
	worker's responses become more specialized and diverse;
  }
\end{itemize}

@@

%\subsection{Performance during repetitive tasks}
%Studies of worker performance during repetitive work have been studied 
%in the context of long-running monitoring tasks, such as those required
%of some facility operators.
%Studies show that performance tends to decline, in terms of
%lengthening reaction time and increased rates of error, as a function of 
%time-on-task \cite{pattyn2008psychophysiological}.  In such 
%contexts, interruptions may actually serve to restore mental attention.
%Studies have shown that improved recall during tasks that were 
%interrupted.  
%
%These studies illustrate the impact of task-duration and
%repetition on performance.  However, the
%relatively low-input monitoring tasks involved in such studies are very
%different from typical microtasks, which require continuous cognitive 
%effort and input from the worker.
%
%In the microtask setting, one study investigated the effect of delays
%and interruptions introduced into a microtask setting.  This study
%found that interruptions and delays
%leading to a significant increase in the time needed to complete the
%interrupted task once resumed.
%However, the researchers did not investigate
%whether interruptions could affect the content of responses.
%
%Here we focus on how the content of earlier tasks can influence responses
%to tasks later ones.  Because qualitative judgment tasks are difficult
%to automate, but often easy for people to perform, many microtasks are of 
%this kind.  We hypothesize that such tasks are highly susceptible to 
%priming effects, and that in the repetitive pattern of microtask work
%(and most crowdsourced work), earlier tasks may act as primes to later 
%ones, and thereby introduce singificant amounts of bias.

@@

Determining the strength of intertask effects amounts to measuring a 
distance, or \textit{divergence}, between response distributions.
We will present a method for bounding a kind of divergence known as 
\textit{total variational distance}\footnote{
  Other formulations such as the Kullback-Leibler and 
  Jensen-Shannon divergence can be related to the total variational
  distance.
}, which we will henceforth denote by $\theta$.
The value of $\theta$ between two distributions $P$ and $Q$ 
is the fraction under the graph of $P$ that does not overlap with that
under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
Formally:
\begin{align}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
	\label{eq:theta}
\end{align}
Where $p(x)$ and $q(x)$ are the respective probabilities 
that a worker submits response $x$, from a set of possible responses 
$\mathcal{X}$, under distributions $P$ and $Q$.
The divergence is constrained to 
$0 \leq \theta \leq 1$ (or from 0 to 100\%).
When $\theta = 100\%$, the distributions do not overlap at all.  
When $\theta = 0\%$, the distributions are identical.
For reference, the distributions plotted in 
Figure~\ref{fig:l1_example}A and B have $\theta=50\%$ and $\theta=30\%$ 
respectively.

@@

Of course, neither $p_1(x)$ nor $p_2(x)$ are known.  But, on seeing $x$,
the probability that such a classifier would be correct is:
\begin{align}
  \mathrm{Pr}\{\mathrm{correct}|x\} = \frac{1}{2} 
	+ \frac{|p_0(x) - p_1(x)|}{2(p_0(x) + p_1(x))}
\end{align}
Summing over all possible responses that a worker could provide, 
$x \in \mathcal{X}$, weighted by the probability of observing $x$, 
we obtain the accuracy of the optimal classifier:
\begin{align}
\eta_* 
  &= \sum_{x\in\mathcal{X}} 
	\mathrm{Pr}\{\mathrm{correct}|x\}\mathrm{Pr}\{x\} \\
  &= \sum_{x\in\mathcal{X}} 
	\left(
	\frac{1}{2} + \frac{|p_0(x) - p_1(x)|}{2(p_0(x) + p_1(x))}
  \right) \left( 
	\frac{p_0(x) + p_1(x)}{2} 
  \right) \\
  &= \frac{1 + \theta}{2}
\end{align}
Since no classifier can be more accurate than an optimal classifier,
it follows that, for any \textit{practical classifier} 
with accuracy $\eta_\mathcal{A}$, the bound 
$\theta \geq 2\eta_\mathcal{A} -1$ holds.

@@

The first experiment we performed consisted of two sub-experiments which
we will call ``intertask'' and ``framing'', because they are respectively
designed to measure intertask and framing effects.  The experiment was 
performed on MTurk using 476 workers.  Workers
could only participate once in a given experiment, and could only 
participate in one of the experiments we present here.

The experiment was conducted using a single HIT\footnote{
  On MTurk, a HIT (or Human Intelligence Task) is the smallest 
  assignable unit of work.  The use of ``Task'' in HIT differs from that
  used here; here labeling a single image is considered to be one ``task'',
  and so a HIT is actually composed of 10 tasks.
}.  Workers who accepted the HIT were randomly assigned to one of the two
sub-experiments.  Both sub-experiments consisted of two treatments, which
we call ``food'' and ``culture'', and workers were also randomly 
assigned to a treatment.  In both treatments of both sub-experiments,
workers were asked to perform ten image-labeling tasks, each of which 
required the worker to assign five descriptive labels to an image.  
In all cases, the last five tasks were identical among all treatments 
(and across sub-experiments), and were presented in the same order.  
These last five tasks constituted the ``test tasks'', whose distribution
of responses could admit intertask or framing effects.

@@

In the framing sub-experiment, we did not vary the initial tasks, but 
instead, introduced a \textit{framing slide} before the tasks.  
Depending on the treatment, the framing slide read 
``This research is proudly funded by The National Foundation for 
Nutritional Awareness'', or ``\ldots by the Global Foundation for the 
Recognition of Cultures''.  The intention was to frame the task by
providing the name of a (fictitious) funder, while using names that
invite the worker to focus on different aspects of the image content.  
As already mentioned, the test tasks consisted of images depicting meals 
of diverse ethnic origin.

@@

\paragraph{Strength of intertask and framing effects.}
Having affirmed the \textit{existence} of intertask effects, we sought to
measure their strength, i.e. $\theta$.
To measure $\theta$ we created a naive Bayes classifier based on a 
multinomial distribution over the word frequencies in worker's labels, 
and measured it's accuracy using leave-one-out cross-validation.  
We chose the naive Bayes
classifier for three reasons.  First, it performs well even when the 
number of features is large compared to the number of training examples
\cite{bickel2004,hastie2009elements}.  
Second, there are no hyperparameters to 
optimize, which eliminates the need to partition the response data into
dev and test sets.
Third, the conditional independence assumption, normally 
undertaken for pragmatic reasons \cite{Zhang2004562}, 
is probably mild in 
relation to image labels, since they are likely to be less dependent
on one another than in a coherent passage of text.  We repeated our
analysis using a support vector machine and found very similar results.

@@

\pagebreak
\section{Experiment 2}
\subsection{Setup}
In Experiment 2 we again had ``intertask'' and ``framing'' 
sub-experiments, but we included a third sub-experiment, ``echo'', which 
incorporated more extreme framing treatments.  
As before, each sub-experiment had
two treatments, but this time they were ``food'' and ``objects''.
Keeping a food treatment enabled us to perform deeper lexical analysis of 
both experiments (to be discussed in the results for Experiment 2).  
The experiment was again performed using a single HIT on MTurk, 
and involved 1666 workers.
Workers were randomly assigned to a sub-experiment and treatment upon
starting the HIT.

@@

\begin{figure}
	\centering
	\includegraphics[scale=1.05]{figs/specificity.pdf}
	\caption{
		Workers exposed to food (either in framing or initial tasks)
		show a different tendency to focus on food when labeling
		test tasks, and their vocabulary in reference to food is affected.
		In all three plots, positive values indicate a larger quantity for 
		workers from the food treatment.
		(\textbf{A}) Exposing workers to food does not necessarily increase
		the fraction of food references they provide during test tasks.
		(\textbf{B}) The number of unique food-related
		words (richness) was greater for food-exposed workers, 
		except in the 
		case of the framing sub-experiment of Experiment 1 
		(stars indicate the threshold
		for a significant deviation, $\alpha=0.05$). 
		(\textbf{C}) Food-exposed
		workers used more specialized words to refer to food.
		Standard error bars are shown in (\textbf{A}) and (\textbf{C}).
	}
	\label{fig:specificity}
\end{figure}

@@

The above observations regarding lexical richness, suggest that initial 
tasks might influence workers to use more \textit{refined} or 
\textit{specialized} words, when referring to aspects 
of content that had been present in the initial tasks.  
To test this directly, we used the hypernym and hyponym relations in 
WordNet to operationalize the notion of word specialization.  
Within each sub-experiment, we determined the relative specificity
of the food-words, between the treatments using the following equation:
\begin{equation}
	S(P,Q) = \frac{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
	}{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
	},
\end{equation}
where $P$ and $Q$ are sets of words associated to different experimental 
treatments, and $\mathbf{1}_{[w>v]}$ evaluates
to 1 if word $w$ is more specific than (i.e. is a hyponym of) word $v$.
The relative specificity lies within $[-1,1]$; 
we report it as a signed percentage.
In computing this quantity between two treatments, we first computed the 
relative specificity for the treatments separately for each test task, and 
averaged the results obtained across the five test tasks.  To establish
significance, we again used a null model, based on bootstrapping.

@@

However, as we alluded to above, there appears to be countervailing 
factors:
while richness and specialization of food-related words always increased 
(or were not significantly changed) among workers exposed to food in 
initial tasks, the total number of references to food significantly 
\textit{decreased} in one case.  
Here we suspect \textit{negative} priming to be at play.
Negative priming occurs when, after exposure to a stimulus 
considered to be non-salient, subsequent recognition of the stimulus is 
inhibited \cite{mayr2007negative}.  In the case of our image labeling 
tasks, repeated exposure to images depicting food might cause the worker to
stop regarding the basic presence of food as salient, and to direct her 
attention instead to the features that are specific to the food in a given 
image.  This would explain the suppression very generic references to 
food observed in Table~\ref{table:top-words}.  
The balance between the inhibition of generic food-related words, with 
activation of specific ones could lead to more or less food references
overall, so this dual priming mechanism is consistent with our 
observations.  Direct experimentation would be needed to determine whether
priming mechanisms, positive or negative, are in able to explain intertask
effects.

Prior to this study, it was not realized that earlier microtasks could 
have such strong effects on later ones.
But our findings show this is an important design consideration that 
should be considered by anyone using microtask platforms.
The commonly employed practice of randomizing task ordering probably
introduces a significant amount of noise due to intertask effects:
Even chains of two or three similar tasks, which will not be reliably 
eliminated in random permutations, could lead to the levels of influence 
we observed in our experiments.  Preferably, a deeper understanding of 
intertask effects might allow them to be properly controlled.

But perhaps more importantly, our findings show that intertask effects 
might be leveraged achieve greater quality and reproducibility in 
crowdsourcing.
A consistent goal in human computation is the achievement of expert-level
judgments from non-expert workers \cite{kittur2011crowdforge}.  
This has been achieved in some
applications \cite{snow2008cheap,Mortensen20131020,Warby2014385}. 
The distinction between experts and novices is partly attributable
to specialized knowledge and heuristics. 
But experts also simplify tasks by more efficiently directing 
their focus toward salient features \cite{kellman2009perceptual}.  
Using strategic task exposure during training, it might be possible to 
guide workers' focus and salience attribution, enabling expert-level 
judgment in a wider variety of crowdsourced applications.

>>>>

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
\toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is      granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
{\emph{CHI'16}}, May 07--12, 2016, San Jose, CA, USA. \\
Copyright is held by the owner/author(s). Publication rights licensed to ACM. \\
ACM 978-1-4503-3362-7/16/05 \$15.00  \\
DOI http://dx.doi.org/10.1145/2858036.2858490
}
%Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
%http://dx.doi.org/10.1145/2858036.2858490}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

@@

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead 
%\usepackage[T1]{fontenc}
\usepackage{txfonts}
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage[pdftex]{hyperref}
% \usepackage{url}      % llt: nicely formatted URLs
\usepackage{color}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{ccicons}
\usepackage{todonotes}
\usepackage{paralist}

@@

%\CopyrightYear{2016}
%\setcopyright{acmlicensed}
%\conferenceinfo{CHI'16,}{May 07 - 12, 2016, San Jose, CA, USA}
%\isbn{978-1-4503-3362-7/16/05}\acmPrice{\$15.00}
%\doi{http://dx.doi.org/10.1145/2858036.2858490}

@@

\numberofauthors{2}
\author{%
  \alignauthor{
	Edward Newell\\
    \affaddr{School of Computer Science}\\
    \affaddr{McGill University}\\
	\email{\texttt{edward.newell@mail.mcgill.ca}}
  }\\
  \alignauthor{
    Derek Ruths\\
    \affaddr{School of Computer Science}\\
	\affaddr{McGill University}\\
	\email{\texttt{derek.ruths@mcgill.ca}}
  }\\
}

@@

Psychological experiments show that the exposure to stimuli immediately 
before performing a task influences performance, an effect known as 
\textit{priming} 
\cite{Ghuman17062008,BJOP1826,beller1971priming,BJOP1796}.
The effect of priming appears to be stronger when the modality of the
prime is the same as the task \cite{BJOP1796}.
Thus, for the typical microtask worker, who does many similar tasks in
quick succession, there is a potential for earlier tasks to influence
later ones, via priming or other mechanisms.

@@

As our main contributions, we
\begin{compactitem}%[noitemsep,nolistsep]
  \item{
	derive a method for measuring changes in response distributions;
  }
  \item{measure the strength of intertask effects;}
  \item{show that intertask effects are stronger than,
	or on par with framing;}
  \item{
	show that when completing a series of similar microtasks,
	worker's responses become more specialized and diverse;
  }
\end{compactitem}

@@

%\subsection{Performance during repetitive tasks}
%Studies of worker performance during repetitive work have been studied 
%in the context of long-running monitoring tasks, such as those required
%of some facility operators.
%Studies show that performance tends to decline, in terms of
%lengthening reaction time and increased rates of error, as a function of 
%time-on-task \cite{pattyn2008psychophysiological}.  In such 
%contexts, interruptions may actually serve to restore mental attention.
%Studies have shown that improved recall during tasks that were 
%interrupted.  
%
%These studies illustrate the impact of task-duration and
%repetition on performance.  However, the
%relatively low-input monitoring tasks involved in such studies are very
%different from typical microtasks, which require continuous cognitive 
%effort and input from the worker.
%
%In the microtask setting, one study investigated the effect of delays
%and interruptions introduced into a microtask setting.  This study
%found that interruptions and delays
%leading to a significant increase in the time needed to complete the
%interrupted task once resumed.
%However, the researchers did not investigate
%whether interruptions could affect the content of responses.
%
%Here we focus on how the content of earlier tasks can influence responses
%to tasks later ones.  Because qualitative judgment tasks are difficult
%to automate, but often easy for people to perform, many microtasks are of 
%this kind.  We hypothesize that such tasks are highly susceptible to 
%priming effects, and that in the repetitive pattern of microtask work
%(and most crowdsourced work), earlier tasks may act as primes to later 
%ones, and thereby introduce significant amounts of bias.

@@

Determining the strength of intertask effects amounts to measuring a 
distance, or \textit{divergence}, between response distributions.
We will present a method for bounding a kind of divergence known as 
\textit{total variational distance}\footnote{
  Other formulations such as the Kullback-Leibler and 
  Jensen-Shannon divergence can be related to the total variational
  distance.
}, which we will henceforth denote by $\theta$.
The value of $\theta$ between two distributions $P$ and $Q$ 
is the fraction under the graph of $P$ that does not overlap with that
under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
Formally:
\begin{align}
  \theta = \frac{1}{2}\sum_{x \in \mathcal{X}} \left| p(x) - q(x) \right|,
	\label{eq:theta}
\end{align}
Where $p(x)$ and $q(x)$ are the respective probabilities 
that a worker submits response $x$, from a set of possible responses 
$\mathcal{X}$, under distributions $P$ and $Q$.
The divergence is constrained to 
$0 \leq \theta \leq 1$ (or from 0 to 100\%).
When $\theta = 100\%$, the distributions do not overlap at all.  
When $\theta = 0\%$, the distributions are identical.
For reference, the distributions plotted in 
Figure~\ref{fig:l1_example}A and B have $\theta=50\%$ and $\theta=30\%$ 
respectively.

@@

Of course, neither $p_1(x)$ nor $p_2(x)$ are known.  But, on seeing $x$,
the probability that such a classifier would be correct is:
\begin{align}
  \mathrm{Pr}\{\mathrm{correct}|x\} = \frac{1}{2} 
	+ \frac{|p_1(x) - p_2(x)|}{2(p_1(x) + p_2(x))}
\end{align}
Summing over all possible responses that a worker could provide, 
$x \in \mathcal{X}$, weighted by the probability of observing $x$, 
we obtain the accuracy of the optimal classifier:
\begin{align}
\eta_* 
  &= \sum_{x\in\mathcal{X}} 
	\mathrm{Pr}\{\mathrm{correct}|x\}\mathrm{Pr}\{x\} \\
  &= \sum_{x\in\mathcal{X}} 
	\left(
	\frac{1}{2} + \frac{|p_1(x) - p_2(x)|}{2(p_1(x) + p_2(x))}
  \right) \left( 
	\frac{p_1(x) + p_2(x)}{2} 
  \right) \\
  &= \frac{1 + \theta}{2}
\end{align}
Since no classifier can be more accurate than an optimal classifier,
it follows that, for any \textit{practical classifier} 
with accuracy $\eta_\mathcal{A}$, the bound 
$\theta \geq 2\eta_\mathcal{A} -1$ holds.

@@

The first experiment we performed consisted of two sub-experiments which
we will call ``intertask'' and ``framing'', because they are respectively
designed to measure intertask and framing effects.  The experiment was 
performed on MTurk using 476 workers.  Workers
could only participate once in a given experiment, and could only 
participate in one of the experiments we present here.  Workers were 
required to have had 90\% of their previously submitted work on Mturk 
accepted by other requesters to participate.  No other screening 
was applied to workers.

The experiment was conducted using a single HIT\footnote{
  On MTurk, a HIT (or Human Intelligence Task) is the smallest 
  assignable unit of work.  The use of ``Task'' in HIT differs from that
  used here; here labeling a single image is considered to be one ``task'',
  and so a HIT is actually composed of 10 tasks.
}.  Workers who accepted the HIT were randomly assigned to one of the two
sub-experiments.  Both sub-experiments consisted of two treatments, which
we call ``food'' and ``culture'', and workers were also randomly 
assigned to a treatment, resulting in 119 workers per treatment.  
In both treatments of both sub-experiments,
workers were asked to perform ten image-labeling tasks, each of which 
required the worker to assign five descriptive labels to an image.  
Labels had to contain at least two letters to be accepted. 
Workers were paid USD\$0.45 for their work.
In all cases, the last five tasks were identical among all treatments 
(and across sub-experiments), and were presented in the same order.  
These last five tasks constituted the ``test tasks'', whose distribution
of responses could admit intertask or framing effects.

@@

In the framing sub-experiment, we did not vary the initial tasks, but 
instead, introduced a \textit{framing slide} before the tasks.  
Depending on the treatment, the framing slide read 
``This research is proudly funded by The National Foundation for 
Nutritional Awareness'', or ``\ldots by the Global Foundation for the 
Recognition of Cultures''.  The intention was to frame the task by
providing the name of a (fictitious) funder, while using names that
invite the worker to focus on different aspects of the image content.  
Initial tasks were still included to ensure that learning or fatigue 
effects were equalized between the sub-experiments.  
For the initial tasks, we used the same images as had been shown to the 
food treatment of the intertask sub-experiment.  
If intertask effects exist, any choice of images for the initial tasks 
will have an effect.  This choice makes the food treatments of both 
sub-experiments very similar, so that the culture treatments of both 
sub-experiments can be viewed as perturbations from a similar baseline.  
The test tasks were the same as for the intertask sub-experiment.

Manual inspection showed that the vast majority of labels were of 
high-quality.  Less than 1\% of submissions were problematic, having
redundant labels or entries that were not English words.
We chose to include all submissions for analysis in the experiments
presented here.

@@

\pagebreak
\paragraph{Strength of intertask and framing effects.}
Having affirmed the \textit{existence} of intertask effects, we sought to
measure their strength, i.e. $\theta$.
To measure $\theta$ we created a naive Bayes classifier based on a 
multinomial distribution over the word frequencies in worker's labels, 
and measured it's accuracy using leave-one-out cross-validation.  
We chose the naive Bayes
classifier for three reasons.  First, it performs well even when the 
number of features is large compared to the number of training examples
\cite{bickel2004,hastie2009elements}.  
Second, there are no hyperparameters to 
optimize, which eliminates the need to partition the response data into
dev and test sets.
Third, the conditional independence assumption, normally 
undertaken for pragmatic reasons \cite{Zhang2004562}, 
is probably mild in 
relation to image labels, since they are likely to be less dependent
on one another than in a coherent passage of text.  We repeated our
analysis using support vector machines and found very similar results.

@@

\section{Experiment 2}
\subsection{Setup}
In Experiment 2 we again had ``intertask'' and ``framing'' 
sub-experiments, but we included a third sub-experiment, ``echo'', which 
incorporated more extreme framing treatments.  
As before, each sub-experiment had
two treatments, but this time they were ``food'' and ``objects''.
Keeping a food treatment enabled us to perform deeper lexical analysis of 
both experiments (to be discussed in the results for Experiment 2).  
The experiment was again performed using a single HIT on MTurk, 
and involved 1666 workers.
Workers were randomly assigned to a sub-experiment and treatment upon
starting the HIT, resulting in 119 workers per treatment.

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.97]{figs/specificity.pdf}
	\caption{
		Workers exposed to food (either in framing or initial tasks)
		showed a different tendency to focus on food when labeling
		test tasks, and their vocabulary in reference to food was affected.
		In all three plots, positive values indicate a larger quantity for 
		workers from the food treatment.
		(\textbf{A}) Exposing workers to food significantly changed the 
		fraction of food references they provide, but did not necessarily 
		\textit{increase} it.
		(\textbf{B}) The number of unique food-related
		words (richness) was greater for food-exposed workers, 
		except in the 
		case of the framing sub-experiment of Experiment 1 
		(stars indicate the threshold
		for a significant deviation, $\alpha=0.05$). 
		(\textbf{C}) Food-exposed
		workers used more specialized words to refer to food.
		Standard error bars are shown in (\textbf{A}) and (\textbf{C}).
	}
	\label{fig:specificity}
\end{figure}

@@

The above observations regarding lexical richness suggest that initial 
tasks might influence workers to use more \textit{refined} or 
\textit{specialized} words, when referring to aspects 
of content that had been present in the initial tasks.  
To test this directly, we used the hypernym and hyponym relations in 
WordNet to operationalize the notion of word specialization.  
Within each sub-experiment, we determined the relative specificity
of the food-words, between the treatments using the following equation:
\begin{equation}
	S(P,Q) = \frac{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
	}{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
	},
\end{equation}
where $P$ and $Q$ are sets of words associated to different experimental 
treatments, and $\mathbf{1}_{[w>v]}$ evaluates
to 1 if word $w$ is more specific than (i.e. is a hyponym of) word $v$.
The relative specificity lies within $[-1,1]$; 
we report it as a signed percentage.
In computing this quantity between two treatments, we first computed the 
relative specificity for the treatments separately for each test task, and 
averaged the results obtained across the five test tasks.  To establish
significance, we again used a null model, based on bootstrapping.

@@

However, as we alluded to above, there appears to be countervailing 
factors:
while richness and specialization of food-related words always increased 
(or were not significantly changed) among workers exposed to food in 
initial tasks, the total number of references to food significantly 
\textit{decreased} in one case.  
Here we suspect \textit{negative} priming to be at play.
Negative priming occurs when, after exposure to a stimulus 
considered to be non-salient, subsequent recognition of the stimulus is 
inhibited \cite{mayr2007negative}.  In the case of our image labeling 
tasks, repeated exposure to images depicting food might cause the worker to
stop regarding the basic presence of food as salient, and to direct her 
attention instead to the features that are specific to the food in a given 
image.  This would explain the suppression of very generic references to 
food observed in Table~\ref{table:top-words}.  
The balance between the inhibition of generic food-related words, and the 
activation of specialized ones, could lead to more or less food references
overall, so this dual priming mechanism is consistent with our 
observations.  Direct experimentation is needed to determine whether
priming mechanisms, positive or negative, can explain intertask
effects.

Prior to this study, it was not realized that earlier microtasks could 
have such strong effects on later ones.
But our findings show this is an important design factor that 
should be considered by anyone using microtask platforms.
The commonly employed practice of randomizing task ordering probably
introduces a significant amount of noise due to intertask effects:
even chains of two or three similar tasks, which will not be reliably 
eliminated in random permutations, could lead to the levels of influence 
we observed in our experiments.  Preferably, a deeper understanding of 
intertask effects might allow them to be properly controlled.

But perhaps more importantly, our findings show that intertask effects 
might be leveraged obtain greater quality and reproducibility in 
crowdsourcing.
A consistent goal in human computation is the elicitation of expert-level
judgments from non-expert workers \cite{kittur2011crowdforge}.  
This has been achieved in some
applications \cite{snow2008cheap,Mortensen20131020,Warby2014385}. 
The distinction between experts and novices is partly attributable
to specialized knowledge and heuristics. 
But experts also simplify tasks by more efficiently directing 
their focus toward salient features \cite{kellman2009perceptual}.  
Using strategic task exposure during training, it might be possible to 
guide workers' focus and salience attribution, enabling expert-level 
judgment in a wider variety of crowdsourced applications.
